Applied Measure Theory for Probabilistic Modeling

### 2022-05-12 paper/paper.tex
edits

We'll now describe some foundations to help the reader get a deeper understanding of our approach, in particular what measures and probability distributions are and how they relate to notions such as the probability of something happening in the real world or the notion of volume of the space we are living in.

@@

From a computational perspective,
a Julia function taking only an \verb|rng::AbstractRNG| argument, making a number of calls to \verb|rand(rng)|, and returning a value $x\in X$ is a random variable $\bX \colon \Omega\to X$.
A simple example is  \verb|X(rng=Random.GLOBAL_RNG) = rand(rng, 1:6)|.
While mathematically $\bX$ is a function from $\Omega$, the argument $\omega$ is often hidden like the function argument \verb|rng| of its computational counterpart---not a coincidence.

@@

In \verb|MeasureTheory|, a kernel is represented as either a Julia function or a \verb|Kernel| object. The latter pairs a measure constructor with a mapping into its parameter space, and makes the functional relationship between argument of $\kappa$ and the returned measure transparent.

>>>>

We'll now describe some foundations to help the reader get a deeper understanding of our approach, in particular what measures and probability distributions are and how they relate to notions such as the probability of something happening in the real world or the notion of volume of the space we are living in. 
\chad{Above sentence is very long, can we break it up?}

@@

From a computational perspective,
a Julia function taking only an \verb|rng::AbstractRNG| argument, making a number of calls to \verb|rand(rng)|, and returning a value $x\in X$ is a random variable $\bX \colon \Omega\to X$.
A simple example is  
\begin{verbatim}
    X(rng=Random.GLOBAL_RNG) = rand(rng, 1:6)
\end{verbatim}
While mathematically $\bX$ is a function from $\Omega$, the argument $\omega$ is often hidden like the function argument \verb|rng| of its computational counterpart---not a coincidence.

@@

In \verb|MeasureTheory|, a kernel is represented as either a Julia function or a \verb|TransitionKernel| object. The latter pairs a measure constructor with a mapping into its parameter space, and makes the functional relationship between argument of $\kappa$ and the returned measure transparent.
